My title

### 2024-11-04 paper/paper.qmd
updated refrences

library(tidyverse)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)
library(knitr)
library(webshot2)

@@

The aggregated dataset containing the polling data for the 2024 U.S. election was sourced from FiveThrityEight ().
We use the statistical programming language R [@citeR] and packages the ...
to download, analyze, and model the data.

@@

```{r}
#| label: fig-state-vs-size
#| fig-cap: This chart displays the total sample size per state for survey data, ordered from highest to lowest sample size.
#| echo: false
#| warning: false
#| message: false

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)
library(knitr)
library(webshot2)

@@

The aggregated dataset containing the polling data for the 2024 U.S. election was sourced from FiveThrityEight () and all analysis was performed using R @citeR and the following packages: [@citeR] and the following packages: tidyverse [@tidyverse], dplyr [@dplyr], janitor [@janitor], testthat [@testthat], arrow [@arrow], here [@here], rstanarm [@rstanarm], bayesplot [@bayesplot], gt [@gt], kableExtra [@kableExtra], knitr [@knitr], and webshot2 [@webshot2].

@@

```{r}
#| label: fig-state-vs-size
#| fig-cap: This chart displays the total sample size per state for survey data, ordered from highest to lowest sample size.
#| echo: false
#| warning: false
#| message: false
#| fig-height: 6
#| fig-width: 8
#| fig-pos: 'H'
